\thesistitle

### 2019-04-22 sattose/paper.tex
Clone Detection

\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{twocolpceurws}

@@

\section{First Level Heading}

First level headings are all flush left, initial caps, bold and in point
size 12. One line space before the first level heading and $1/2$ line
space after the first level heading.

>>>>

\documentclass[a4paper]{article}
\usepackage{graphicx}
\usepackage{twocolpceurws}
\usepackage{float}
\usepackage{hyperref}

@@

In this research, we focus on formalizing the refactoring process of dealing with duplication in code. We will measure open source projects from the We will show the improvement of the metrics over various open source and industrial projects. Likewise, we will perform an estimation of the development costs that are saved by using the proposed solution. We will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}. However, most practises used in this thesis will also be applicable with other object-oriented languages, like C\#.

\section{Clone Detection}
As duplication in source code is a serious problem in many software systems, there are a lot of researches that look into code clones. Many tools have been proposed to detect various types of code clones. Two surveys of modern clone detection tools \cite{sheneamer2016survey, svajlenko2014evaluating} together show an overview of the most-popular clone detection tools up until 2016. To be able to refactor detected clones, it is useful to have the ability to rewrite the AST. We considered a set of clone detection tools for their ability to support the refactoring process automatically. None of the tools we consider seemed completely fit for this purpose, so we decided to implement our own clone detection tool: CloneRefactor\footnote{CloneRefactor (WIP) is available on GitHub: \url{https://github.com/SimonBaars/CloneRefactor}}.

\subsection{CloneRefactor}
A 2016 survey by Gautam \cite{gautam2016various} focuses more on various techniques for clone detection. For our tool we decided to combine AST and Graph based approaches for clone detection, similar to Scorpio (which is a clone detection tool that's part of TinyPDG: a library for building intraprocedural program dependency graphs for Java programs). We decided to base our tool on the JavaParser library \cite{tomassetti2017javaparser}, as it supports rewriting the AST back to Java code. We then collect each statement and declaration (ommitting their child statements and declarations) and compare those to find duplicates. This way we build a graph of each statement/declaration linking to each subsequent statement/declaration (horizontally) and linking to each of it's duplicates (verically). This is displayed in figure \ref{fig:clonerefactor}.

\begin{figure}[H]
  \includegraphics[width=1\columnwidth]{img/CodeGraph}
  \caption{Graph representation built by CloneRefactor}
  \label{fig:clonerefactor}
\end{figure}

### 2019-04-22 sections/introduction.tex
Clone Detection

In this research, we will focus on formalizing the refactoring process of dealing with duplication in code. We will show the improvement of the metrics over various open source and industrial projects. Likewise, we will perform an estimation of the development costs that are saved by using the proposed solution. We will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}. However, most practises used in this thesis will also be applicable with other object-oriented languages, like C\#

@@

\section{Contributions}
Our research makes the following contributions:
\begin{enumerate}
	\item 1
	\item 2
	\item 3
\end{enumerate}

>>>>

In this research, we focus on formalizing the refactoring process of dealing with duplication in code. We will measure open source projects from the We will show the improvement of the metrics over various open source and industrial projects. Likewise, we will perform an estimation of the development costs that are saved by using the proposed solution. We will lay the main focus on the Java programming language as refactoring opportunities do feature paradigm and programming language dependent aspects \cite{choi2011extracting}. However, most practises used in this thesis will also be applicable with other object-oriented languages, like C\#.

@@

\section{Contributions}
Our research makes the following contributions:
\begin{enumerate}
	\item We deliver several novel measurements regarding code clones on a large corpus of Java projects.
	\item We deliver a novel clone detection tool that finds refactorable clones in Java.
	\item We deliver a novel clone refactoring tool that suggests refactorings to be applied, and applies these refactorings.
	\item We give further recommendations in how refactoring can be automatically applied to improve maintainability in software projects.
\end{enumerate}
